Depression and suicidality as costly signals of need

### 2021-04-15 Paper.rmd
Added reddit subreddit

---
title: "Depression and suicidality as costly signals of need"
author: "Michael R. Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
always_allow_html: true
output: 
  bookdown::word_document2:
    number_sections: false
bibliography: MTBib.bib
csl: apa-6th-edition.csl
---

@@

The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to reddit.com (N=28) that used draft versions of 3 vignettes used here, along with the same signals and outcomes. In the MTurk pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan. In the small reddit.com study, participants viewed and responded to two vignettes used here, each with a different signal.

@@

In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first (regardless of the vignette or signal). To avoid such order effects, which are a problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and single signal.

@@

The data associated with this research are available at http://doi.org/10.5281/zenodo.4637904.

>>>>

---
title: "Depression and suicidality as costly signals of need"
author: "Michael R. Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
always_allow_html: true
output: 
  bookdown::html_document2:
    number_sections: false
bibliography: MTBib.bib
csl: apa-6th-edition.csl
---

@@

The current study is a refinement of a large MTurk experimental vignette pilot study (N=`r nrow(signalingdata2018b)`) that used a different vignette but very similar signals and outcomes, and a much smaller pilot study posted to [reddit.com/r/SampleSize/](https://www.reddit.com/r/SampleSize/) (N=28) that used draft versions of 3 vignettes used here, along with the same signals and outcomes. In the MTurk pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan. In the small reddit.com study, participants viewed and responded to two vignettes used here, each with a different signal.

@@

In the reddit.com pilot study, participants viewed two vignettes (with different signals in each one), and responded with lower belief to the second vignette compared to the first (regardless of the vignette or signal). To avoid such order effects, which are a common problem in vignette studies that use multiple vignettes [@su2020], we decided to present each participant in the current study with a single vignette and signal.

@@

The data are available at http://doi.org/10.5281/zenodo.4637904
